%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[scale=0.90]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{12cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------


\email{sn513@cam.ac.uk}
\homepage{https://www.ch.cam.ac.uk/person/sn513}{https://www.ch.cam.ac.uk/person/sn513} 
%\extrainfo{Date Of Birth: 27/6/1986, Nationality: Indian, Visa: Tier 1 (till March, 2023)}

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\section{List of publications}
\cvitem{1}{\textbf{S. Neelamraju},  J. C. Sch{\"o}n, K. Doll and M. Jansen, Ab initio and empirical energy landscapes of (MgF$_2$)$_n$ clusters (n = 3,4),  Phys. Chem. Chem. Phys. 14, 1223-1234 (2012)}
\cvitem{2}{\textbf{S. Neelamraju},  A. Bach, J. C. Sch\"on,  D. Fischer and M. Jansen, A theoretical and experimental study of the  Raman spectra of MgF$_2$ clusters and solids,  J. Chem. Phys. 137, 194319 (2012)}
\cvitem{3}{R. Hundt, J. C. Sch{\"o}n, \textbf{S. Neelamraju}, J. Zagorac and M. Jansen, CCL - an algorithm for the efficient comparison of clusters, J. Appl. Cryst. 46, 587-593 (2013)}
\cvitem{4}{X. Mu,\textbf{S. Neelamraju}, W. Sigle, J. C.  Sch\"on, A. Bach, D. Fischer, M. Jansen and P. A. Van Aken, Evolution of order in amorphous-to-crystalline phase transformation of MgF$_2$, J. Appl. Cryst. 46, 1105-1116 (2013)}
\cvitem{5}{\textbf{S. Neelamraju}, J. C. Sch\"on and M. Jansen, Atomistic Modeling of the Low-Temperature Atom-Beam Deposition of Magnesium Fluoride, Inorg. Chem. 54 (3), 782-791 (2014)}
\cvitem{6}{\textbf{S. Neelamraju}, M. T. Oakley and R. L. Johnston, Chiral effects on helicity studied via the energy landscape of short (d, l)-alanine peptides, J. Chem. Phys. 143, 165103 (2015) }
\cvitem{7}{\textbf{S. Neelamraju}, J. C. Sch\"on and R. L. Johnston, A threshold-minimization scheme for exploring the energy landscape of biomolecules: Application to a cyclic peptide and a disaccharide, J. Chem. Theory Comput.,12 (5),2471-2479 (2016)}
\cvitem{8}{\textbf{S. Neelamraju}, C. Oligschleger and J. C. Sch\"on, The threshold algorithm: Description of the methodology and new developments, J. Chem. Phys.,147,152713 (2017) (\textbf{Editors' Choice})}
\cvitem{9}{\textbf{S. Neelamraju},  S. Gosavi and D. J. Wales, Energy landscape of designed protein Top7, J. Phys. Chem. B., 122(51), 12282-12291 (2018)}
\cvitem{10}{\textbf{S. Neelamraju},  D. J. Wales and S. Gosavi, Go-kit: Enabling Energy Landscape Exploration of Proteins, J. Chem. Inf. Model, 59(5),1703-1708 (2019)}
\cvitem{11}{\textbf{S. Neelamraju},  S. Gosavi and D. J. Wales, Energy landscapes of proteins with trefoil and figure-of-eight knots(in preparation)}
\cvitem{12}{\textbf{S. Neelamraju},Modeling synthesis route of MgF$_2$ via the LT-ABD method (Thesis published as book by SVH-Verlag).}


\section{List of Conferences/Workshops}
\cvitem{2019}{Energy landscapes conference, Belgrade, Serbia.(Speaker)}
\cvitem{2019}{Proteins: Gordon Research Seminar, Holderness, New Hampshire, US. (Speaker)}
\cvitem{2019}{Proteins: Gordon Research Conference, Holderness, New Hampshire, US. (Poster)}
\cvitem{2018}{Methods and applications of crystal structure prediction, Faraday Discussions, Cambridge, UK.(Delegate)}
\cvitem{2018}{Energy landscapes conference, Kalamata, Greece.(Poster)}
\cvitem{2017}{Energy landscapes conference, Goa, India (Speaker).}
\cvitem{2016}{Third International Symposium on Protein Folding and Dynamics, Bangalore, India (Poster, Best poster award).}
\cvitem{2016}{Energy landscapes: Theory and applications, Porquerolles, France (Speaker). }
\cvitem{2015}{Invited speaker, Centre for Complexity Science, University of Warwick, "Complex energy landscapes in chemistry''. }
\cvitem{2015}{Invited speaker, "3rd International Conference: Serbian Society for Ceramic Materials" 15-17th June, Belgrade, Serbia. (Speaker)}
\cvitem{2015}{``The 46th British Association for Crystal Growth Annual Conference'', Queen Mary University, London, UK. (Presented two independent talks).}
\cvitem{2014} {Energy landscapes conference, Durham, UK. (Poster)}
\cvitem{2014} {``Simulation of the deposition and growth of nanocrystalline MgF$_2$ films via the low-temperature atom beam deposition method'', DPG, Dresden. (Speaker)}
\cvitem{2013} {Energy Landscapes Conference, Telluride Science Research Center, Telluride, Colorado, US.(Speaker, absent)}
\cvitem{2012}{SPP 1415 (High-Priority Program), Nonequilibrium crystalline phases: theory and experiment, Darmstadt, Germany.(Speaker)}	
\cvitem{2012}{SPP 1415 (High-Priority Program), Nonequilibrium crystalline phases: theory and experiment, Boppard, Germany. (Speaker)}	
\cvitem{2012}{European Science Foundation Energy Landscapes Conference, Obergurgl, Austria. (Poster)}
\cvitem{2011}{X. Mu , W. Sigle, A. Bach, D. Fischer, N. Toto, \textbf{S. Neelamraju}, J. C. Sch{\"o}n, M. Jansen, and P. A. van Aken, Electron diffraction  analysis of the structural evolution of MgF$_2$ from an amorphous phase to a polycrystalline modification, Microscopy Conference MC2011 in Kiel, Germany. }
\cvitem{2011}{Workshop on ``Computer methods in crystal structure systematics", Stuttgart}
\cvitem{2011}{SPP 1415 (High-Priority Program), Nonequilibrium crystalline phases: theory and experiment, Eisenach, Germany.(Speaker)}
\cvitem{2009}{Workshop on ``Multiscale Modeling of Heterogeneous Nucleation and Structure Formation in Colloids and Metals", CECAM, Zurich.}

\cleardoublepage 
\end{document}